\hypertarget{time-limit-4-seconds.}{%
\paragraph{Time Limit: 4 seconds.}\label{time-limit-4-seconds.}}

\hypertarget{memory-limit-512-mb.}{%
\paragraph{Memory Limit: 512 MB.}\label{memory-limit-512-mb.}}

\hypertarget{statement}{%
\subsection{Statement:}\label{statement}}

C-3IC has come up with a new hypothesis, he believes that for every
positive integer \(n\), and every pair of integers \((i, j)\), such that
\(1 \leq i \leq j \leq n\) the following statement it's true:

\(\gcd {(i, n)} \cdot \gcd {(j, n)} = \gcd {(i \cdot j, n)}\).

C-3IC ran to his PC to test his hypothesis by stress testing, he quickly
noticed that for an integer \(n\) his hypothesis was valid only in some
pairs \((i, j)\), disappointed for not discovering a new theorem, he
wants to analyze the properties of the pairs of numbers that satisfy his
hypothesis for some integers \(n\), and asks you to solve the following
task:

Given a positive integer \(n\), find the number of pairs of integers
\((i, j)\) such that \(1 \leq i \leq j \leq n\) and
\(\gcd {(i, n)} \cdot \gcd {(j , n)} = \gcd {(i \cdot j, n)}\).

There will be \(T (1 \leq T \leq 10 ^ 6)\) test cases per file, in each
one of them will be given an integer
\(n (1 \leq n \leq 4 \cdot 10 ^ 6)\).

\hypertarget{subtasks}{%
\subsubsection{Subtasks:}\label{subtasks}}

\begin{itemize}
\item
  Subtask 1: \(1 \leq T \leq 40\), \(1 \leq n \leq 40\). ( 5 points )
\item
  Subtask 2: \(1 \leq T \leq 100\), \(1 \leq n \leq 10 ^ 5\), The
  smallest divisor of \(n\) is guaranteed to be greater than \(100\). (
  19 points )
\item
  Subtask 3: \(1 \leq T \leq 10^4\), \(1 \leq n \leq 10 ^ 5\), It is
  guaranteed that there will be a prime number \(p\), such that
  \(p^k = n\) for a positive integer \(k\). ( 22 points )
\item
  Subtask 4: \(1 \leq T \leq 10 ^ 5\), \(1 \leq n \leq 10 ^ 5\). ( 25
  points )
\item
  Subtask 5: \(1 \leq T \leq 10 ^ 6\), \(1 \leq n \leq 4 * 10 ^ 6\). (
  29 points )
\end{itemize}

\hypertarget{input-format}{%
\subsubsection{Input format:}\label{input-format}}

The first line of input will contain an integer \(T\), the number of
test cases.

Then there will be \(T\) lines, each one with an integer \(n\).

\hypertarget{output-format}{%
\subsubsection{Output format:}\label{output-format}}

Output \(T\) lines, each one with an integer, the solution of the
problem for each case.

\hypertarget{sample-input}{%
\subsubsection{Sample input:}\label{sample-input}}

\begin{verbatim}
6
1
2
3
4
5
10000
\end{verbatim}

\hypertarget{sample-output}{%
\subsubsection{Sample output:}\label{sample-output}}

\begin{verbatim}
1
2
5
8
14
46047940
\end{verbatim}
